opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-05-14 chapters/01_introduction.tex
Included previous work on crystal structure information prediction

Machine learning has the potential to speed up the manual analysis of powder diffractograms and keep pace with an automated high-throughput experimentation environment. \cite{Agrawal2019, Surdu2023}
Models can be trained to predict crystal structure information directly given a diffractogram, or models can be used to automate the conventional workflow of finding an initial guess and running ML-automated Rietveld refinement. \cite{Surdu2023}    \cite{Feng2019} 
So far, however, due to an absence of labeled datasets with experimental diffractograms, machine learning in this domain has largely relied on diffractograms simulated from known structures (such as from the ICSD) or, most recently, from generated synthetic crystals. \cite{Wang2020, Lee2023}

>>>>

Machine learning has the potential to speed up the manual analysis of powder diffractograms and keep pace with an automated high-throughput experimentation environment. \cite{Agrawal2019, Surdu2023}
Models can be trained to predict crystal structure information directly given a diffractogram, or models can be used to automate the conventional workflow of finding an initial guess and running ML-automated Rietveld refinement. \cite{Surdu2023}    \cite{Feng2019} 
So far, however, due to an absence of labeled datasets with experimental diffractograms\cite{Wang2020} , machine learning in this domain has largely relied on diffractograms simulated from known structures\cite{Park2017} \cite{Lee2023} or, most recently, from generated synthetic crystals. \cite{Schopmans2023}
